Hazelnut: A Bidirectionally Typed \\ Structure Editor Calculus

### 2016-05-04 hazelnut-popl17.tex
added TODO to cite andy ko's paper on design requirements

TODO: cite http://cseweb.ucsd.edu/~lerner/pb.html

>>>>

TODO: cite \url{http://cseweb.ucsd.edu/~lerner/pb.html}

TODO: cite \url{http://delivery.acm.org/10.1145/1060000/1056965/p1557-ko.pdf?ip=73.154.143.34&id=1056965&acc=AUTHOR-IZED&key=4D4702B0C3E38B35%2E4D4702B0C3E38B35%2E4D4702B0C3E38B35%2EC2CC0A83071F7605&CFID=780613712&CFTOKEN=33786941&__acm__=1462392463_f29fc98965004c61bfb1291d07756a23}
